Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-05-27 src/tex/ms.tex
Built the article with the main corner plot.

\shorttitle{Galaxy Catalogues with Normalizing Flows}
\shortauthors{Crenshaw et al.}

@@

@@

The final layer is an RQ-RSC, described in detail in Section \ref{sec:rq-rsc}.
This layer performs the heavy lifting of transforming the data distribution into the uniform latent distribution.
We use $D=7$ layers to transform all 7 dimensions of our data, and set $B=5$ to match the support of the latent distribution.
We use the coupling function (with two hidden layers of 128 neurons) described in \citet{durkan2019}.
We use $K=16$ spline knots \note{check this}.

@@

We assess the results by drawing $10^4$ galaxies from the trained flow, and plotting their distribution against  $10^4$ galaxies from the test set (Figure \note{X}).
We see that the normalizing flow has done an excellent job of reproducing the distribution of DESC DC2, without any unusual artifacts or outliers.
We note that these results were obtained without any extensive hyperparameter search, and that very similar (slightly worse results) are obtained without the \texttt{ColorTransform} bijection, demonstrating the flexibility of the method to adapt to unseen data sets.

>>>>

\shorttitle{Modeling Galaxy Catalogues with Normalizing Flows}
\shortauthors{Crenshaw et al.}

@@

\begin{figure*}[t!]
    \script{plot_main_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/main_galaxy_corner.pdf}
        \caption{
            Distribution of the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise disttribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:main-corner}
    \end{centering}
\end{figure*}

@@

The final layer is an RQ-RSC, described in detail in Section \ref{sec:rq-rsc}.
This layer performs the heavy lifting of transforming the data distribution into the uniform latent distribution.
We use $D=7$ layers to transform all 7 dimensions of our data, and set $B=5$ to match the support of the latent distribution.
We use the coupling function (with two hidden layers of 128 neurons) described in \citet{durkan2019}.
We use $K=16$ spline knots.

@@

We assess the results by drawing $10^4$ galaxies from the trained flow, and plotting their distribution against  $10^4$ galaxies from the test set (Figure \ref{fig:main-corner}).
We see that the normalizing flow has done an excellent job of reproducing the distribution of DESC DC2, without any unusual artifacts or outliers.
We note that these results were obtained without any extensive hyperparameter search, and that very similar (slightly worse results) are obtained without the \texttt{ColorTransform} bijection, demonstrating the flexibility of the method to adapt to unseen data sets.
